Variability analysis 1

### 2022-07-07 experiment-1/analysis/stats/variability.Rmd
edit x/y axis labels
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

ggplot(ioi_cv_subject, aes(x = Condition, y = MeanCV, color = Condition)) +
  geom_boxplot() +
  geom_line(aes(group = SubNr), size = 0.4, color = "gray") +
  geom_point(aes(color = Condition)) +
  facet_grid(. ~ Skill) +
  theme_pubr()
```

@@

ggplot(ioi_tra_subject, aes(x = Condition, y = Mean, color = Condition)) +
  geom_boxplot() +
  geom_line(aes(group = SubNr), size = 0.4, color = "gray") +
  geom_point(aes(color = Condition)) +
  facet_grid(. ~ Skill) +
  theme_pubr()
```

@@

# effect size
wilcoxeff_art_tra <- ioi_tra_subject[Skill == "articulation"] %>% wilcox_d(Mean ~ Condition, paired = TRUE)
wilcoxeff_art_tra
```

>>>>

ggplot(ioi_cv_subject, aes(x = Condition, y = MeanCV, color = Condition)) +
  geom_boxplot() +
  geom_line(aes(group = SubNr), size = 0.4, color = "gray") +
  geom_point(aes(color = Condition)) +
  labs(y = "CVs") +
  facet_grid(. ~ Skill) +
  theme_pubr()
```

@@

ggplot(ioi_tra_subject, aes(x = Condition, y = Mean, color = Condition)) +
  geom_boxplot() +
  geom_line(aes(group = SubNr), size = 0.4, color = "gray") +
  geom_point(aes(color = Condition)) +
  labs(y = "IOIs (ms)") +
  facet_grid(. ~ Skill) +
  theme_pubr()
```

@@

# effect size
wilcoxeff_art_tra <- ioi_tra_subject[Skill == "articulation"] %>% wilcox_effsize(Mean ~ Condition, paired = TRUE)
wilcoxeff_art_tra
```
